---
title: "Lab Week 8"
author: "Emma Siegfried"
date: "March 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Load Packages
```{r}
library(ggplot2)
library(dplyr)
library(readr)
library(sf)
library(tmap)
library(leaflet)
library(spatstat)
library(maptools)
```

###Column graph of TX oil spills
```{r, message=FALSE}

oil_spills <- read_csv("oil_spills.csv")

df <- oil_spills %>% 
  filter(`Accident State` == "TX" & `Accident Year` < 2017) %>% 
  group_by(`Accident Year`) %>% 
  summarise(Loss = sum(`Net Loss (Barrels)`))

colnames(df) <- c("Year", "Loss")

ggplot(df, aes(x=Year, y=Loss))+
  geom_col()+
  theme_classic()

```

###Leaflet plot of spill locations in TX in 2016
```{r}

df_loc <- oil_spills %>% 
  filter(`Accident State` == 'TX' & `Accident Year`== 2016) %>% 
  select(Latitude, Longitude, `Net Loss (Barrels)`)

colnames(df_loc) <- c("latitude", "longitude", "net_loss")

#Have R recognize this data as spatial info

oil_sf <- st_as_sf(df_loc, coords = c("longitude", "latitude"), crs = 4326) #now R knows it's spatial

class(oil_sf) #the first thing is "sf", meaning spatial features

```

```{r map}

leaflet(oil_sf) %>% 
  addTiles() %>% 
  addMarkers()


```

##tmap plot with the Texas state shapefile
```{r}

states <- st_read(dsn = ".", layer = "states") #the dsn="." tells it to get everything from the working directory that meets the "layer" requirement

tex_border <- states %>% 
  filter(STATE_NAME == "Texas") %>% 
  st_transform(4326) #this ensures the spatial data will use the same coordinates as all the other files

plot(tex_border)

tm_shape(tex_border)+
  tm_polygons()+
  tm_shape(oil_sf)+
  tm_dots(size = 0.3)


```

###Convert the data to spatial points patterns (combination of point data and the bounding window)

```{r}
#We need to convert to point pattern data with a window

#1) convert back from simple features to dataframes

spill_sp <- as(oil_sf, "Spatial")

spill_ppp <- as(spill_sp, "ppp") #ppp stands for point pattern

class(spill_ppp) #it is now ppp

tx_sp <- as(tex_border, "Spatial")

tx_owin <- as(tx_sp, "owin") 

#Now we will combine

all_ppp <- ppp(spill_ppp$x, spill_ppp$y, window = tx_owin)


```

###A density plot

```{r}

plot(density(all_ppp, sigma = 0.4)) #sigma changes the density scale/intensity

```

###Quadrat test for spatial evenness
```{r}

#this test evaluated the quadrats and uses chi-squared test to determine if oil spill events are proportional in distribution or not

#H0: data is distributed as CSR (totally random)

oil_qt <- quadrat.test(all_ppp, nx = 5, ny = 5) #nx = 5 is how many regions exist horizontally, ny = vertical regions
oil_qt

#These results show they are not randomly distributed. Reject H0

```
 
```{r}

plot(all_ppp)
plot(oil_qt, add = TRUE, cex = 0.4)

#there are little numbers in each quadrant. if a quadrant isn't whole, then the upper L is actual counts; upper R is expected counts for whole square; bottom # is the standardized metric for the difference between expected count and actual count

```

###G-Function for Nearest Neighbor Analysis

```{r}

r <- seq(0,1, by = 0.01)

#based on a plasun distribution and recognizing the winder you've created, what would this data look like if it was truely CSR data

oil_gfun <- envelope(all_ppp, fun = Gest, r = r, nsim = 100) #Gest is the estimation of G, nsim = #of simulations

#this is pretty quick b/c its just looking at the single distance between each point and its nearest neighbor

#table: theo - theoretical values based on simulation; lo & hi give you the confidence intervals

ggplot(oil_gfun, aes(x = r, y = obs))+
  geom_line(color = "black")+
  geom_line(aes(x = r, y = theo), color = "red")+
  theme_classic()

#This plot tells us that our data has a higher proportion of point pairs with nearest neighbors at shorter distances compared to CSR data. Meaning that the nearest neighbor distances are closer than expected for randomly (CSR) distributed data. So this data is more clustered 

```

###Nearest neighbor using the L-function (Ripley's K, standardized)

```{r}

r2 <- seq(0,3, by = 0.5) #this is saying the sequence will go from 0 to 3, with increments of 0.5

oil_lfun <- envelope(all_ppp, fun = Lest, r = r2, nsim = 20, global = TRUE) #This only involves 20 simulations b/c it takes long. in a real project you would want to do more

ggplot(oil_lfun, aes(x = r2, y = obs))+
  geom_line(color = "black")+
  geom_line(aes(x = r2, y = theo), color = "blue")+
  theme_classic()

#this story is the same as G (as it should)

```















